---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OmopOnPostgres

The goal of OmopOnPostgres is to facilitate working with data in the OMOP CDM format using a PostgreSQL database. The package:

-   **Supports multiple database clients:** Provides flexible approaches for connecting from R to PostgreSQLs.
-   **Simplifies database management:** Facilitates the creation, deletion, and management of OMOP CDM schemas and tables directly from R.
-   **Ensures cross-platform compatibility:** Enables analytic R packages to reliably use `dplyr`/`dbplyr`, supporting cross-platform network studies.
-   **Enhances performance:** Allows for PostgreSQL-specific optimisations of analytic queries.

## Supported drivers

| Driver | Status (Ubuntu / macOS / Windows) |
|:-----------------------------------|:-----------------------------------|
| **RPostgres** | [![Ubuntu RPostgres](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-rpostgres.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-rpostgres.yaml) [![macOS RPostgres](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-rpostgres.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-rpostgres.yaml) [![Windows RPostgres](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-rpostgres.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-rpostgres.yaml) |
| **ADBC** | [![Ubuntu ADBC](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-adbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-adbc.yaml) [![macOS ADBC](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-adbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-adbc.yaml) [![Windows ADBC](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-adbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-adbc.yaml) |
| **ODBC** | [![Ubuntu ODBC](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-odbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-odbc.yaml) [![macOS ODBC](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-odbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-odbc.yaml) [![Windows ODBC](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-odbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-odbc.yaml) |
| **DatabaseConnector** | [![Ubuntu DatabaseConnector](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-databaseconnector.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-databaseconnector.yaml) [![macOS DatabaseConnector](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-databaseconnector.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-databaseconnector.yaml) [![Windows DatabaseConnector](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-databaseconnector.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-databaseconnector.yaml) |
| **DuckDB** | [![Ubuntu DuckDB](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-duckdb.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-duckdb.yaml) [![macOS DuckDB](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-duckdb.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-duckdb.yaml) [![Windows DuckDB](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-duckdb.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-duckdb.yaml) |

## Installation

You can install the development version of OmopOnPostgres from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ohdsi/OmopOnPostgres")
```

## Example

```{r}
library(OmopOnPostgres)
library(OmopSketch)
cdm <- mockPostgresCdmReference(client = "RPostgres", 
                                datasetName = "GiBleed")
summariseOmopSnapshot(cdm) |> 
  tableOmopSnapshot(type = "flextable")
```
