---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OmopOnPostgres

| Platform | Driver | Status |
|:---|:---|:---|
| **Ubuntu** | RPostgres | [![Ubuntu RPostgres](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-rpostgres.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-rpostgres.yaml) |
| **Ubuntu** | adbc | [![Ubuntu adbc](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-adbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-adbc.yaml) |
| **Ubuntu** | odbc | [![Ubuntu odbc](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-odbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/ubuntu-odbc.yaml) |
| **macOS** | RPostgres | [![macOS RPostgres](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-rpostgres.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-rpostgres.yaml) |
| **macOS** | adbc | [![macOS adbc](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-adbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-adbc.yaml) |
| **macOS** | odbc | [![macOS odbc](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-odbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/macos-odbc.yaml) |
| **Windows** | RPostgres | [![Windows RPostgres](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-rpostgres.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-rpostgres.yaml) |
| **Windows** | adbc | [![Windows adbc](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-adbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-adbc.yaml) |
| **Windows** | odbc | [![Windows odbc](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-odbc.yaml/badge.svg)](https://github.com/OHDSI/OmopOnPostgres/actions/workflows/windows-odbc.yaml) |

The goal of OmopOnPostgres is to ...

## Installation

You can install the development version of OmopOnPostgres from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ohdsi/OmopOnPostgres")
```

## Example

```{r example}
library(OmopOnPostgres)
```
